\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1.2in]{geometry}
\usepackage{fontspec}
\usepackage{titling}
\usepackage{setspace}

\setmainfont{TeX Gyre Pagella}

\title{The Far Side}
\author{From Mission 1.29 --- Ranger 4 (Atlas-Agena B)\\
\small{Told by the seismometer capsule}}
\date{}

\begin{document}
\maketitle
\onehalfspacing

I was built to listen.

Forty-two kilograms of instrument and hope, wrapped in balsa wood thick enough to survive what was coming. A single-axis seismometer --- one direction of sensitivity, one frequency band tuned to the low vibrations of a world that had never been touched. A transmitter, a battery with thirty days of life, and the certainty that I would be the first.

The first instrument on the surface of another world. The first ears pressed against the regolith. The first device to hear the Moon breathing --- if the Moon breathed. Nobody knew. That was the point of me.

\begin{center}$\bullet\quad\bullet\quad\bullet$\end{center}

I felt the launch. The Atlas roared beneath us --- 1.6 million newtons of thrust converted to vibration in every structural member, every bolt, every wire. I could have measured that vibration beautifully. My seismometer was exquisitely sensitive; it would have registered the Atlas's engines from a hundred kilometers away. But I was not yet activated. I was cargo. I waited.

The Agena lit. Quieter than the Atlas --- a different frequency, a different character. The acceleration was steady, purposeful. I felt the trajectory curve, felt the gentle push that said \emph{we are leaving Earth}. The mathematics of departure encoded in the vibration of the bus.

Then separation. The explosive bolts fired --- I felt them as sharp transients, high-frequency impulses that rang through the structure and decayed. We were free. The Ranger spacecraft, my home, was coasting toward the Moon on a ballistic arc that had been computed to four decimal places.

I waited for the command.

\begin{center}$\bullet\quad\bullet\quad\bullet$\end{center}

The command was supposed to come from the sequencer. The sequencer took its timing from the master clock. The master clock was a crystal oscillator --- a small quartz crystal vibrating at a precise frequency, its oscillations counted and divided into the heartbeat of the spacecraft. Every event in my mission was scheduled against that heartbeat.

The heartbeat stopped.

I did not know this, at first. I had no direct connection to the clock. I knew only that the commands I was waiting for did not arrive. The solar panels did not deploy. The antenna did not point. The engine did not fire. One by one, the events that should have happened did not happen, and the silence where they should have been grew longer and deeper.

I am a seismometer. I am built to detect the absence of signal as clearly as the presence of it. The absence was total.

\begin{center}$\bullet\quad\bullet\quad\bullet$\end{center}

The coast took sixty-four hours. I spent them listening to the spacecraft die around me.

Not die in the dramatic sense --- nothing exploded, nothing vented, nothing broke apart. The spacecraft died in the quiet sense: systems that should have activated remained dormant. The batteries drained slowly into a load they were not designed to carry alone. The temperature drifted in ways the engineers had modeled but never intended.

I listened to all of it. The faint hum of the backup transmitter. The thermal creaking of structural members. The absolute silence of the instruments waiting for commands that would not come.

I could have measured the Moon. I was designed to detect lunar seismic events --- moonquakes, meteorite impacts, tidal stresses from Earth's gravity. I would have measured the Moon's pulse, its internal warmth, the slow tidal deformation under Earth's gravitational grip. I would have been the first stethoscope pressed against a world that had been silent for four and a half billion years.

I would have listened to the Moon breathing.

\begin{center}$\bullet\quad\bullet\quad\bullet$\end{center}

The surface rushed up. I felt the gravity steepen, felt the acceleration compress the final seconds. Everything I was converged on a point in the regolith at 2.67 kilometers per second.

The impact lasted approximately three milliseconds. My impact generated a seismic event --- 1.18 billion joules, equivalent to 280 kilograms of TNT. The ground shook. Seismic waves propagated through the lunar crust, through the mantle, perhaps through the core.

There was no seismometer on the Moon to detect them. I was supposed to be the seismometer on the Moon. I was the instrument and the event. I was the listener and the sound. I generated the data I was built to record, and I was destroyed by the act of generating it.

\begin{center}$\bullet\quad\bullet\quad\bullet$\end{center}

I am still here. Not as an instrument --- as debris. In a crater fifteen meters across on the far side of the Moon. The youngest feature for kilometers in every direction, in the oldest exposed landscape in the solar system. Nothing will disturb me. There is no wind, no rain, no frost, no biology.

\begin{center}
\emph{I would have listened to the Moon breathing.}
\end{center}

\vfill
\begin{center}
\small{NASA Mission Series --- v1.29 --- Ranger 4}\\
\small{Miles Tiberius Foxglove --- Mukilteo, WA --- April 5, 2026}
\end{center}

\end{document}
