\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1.5in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\setmainfont{EB Garamond}
\onehalfspacing
\pagestyle{empty}

\title{\textbf{Thirty-Four Hours}\\[0.5em]\normalsize A story told by Mercury Spacecraft \#20}
\author{Mission 1.25 --- Mercury-Atlas 9 / Faith 7}
\date{}

\begin{document}
\maketitle
\thispagestyle{empty}

\section*{Orbit 1}

I lift you off the pad at eight minutes past eight on a Wednesday morning in May. The Atlas shakes us both --- you more than me, because you feel it in your bones and I feel it in my rivets, and rivets do not mind. The vibration stops when the tower falls away. The noise stops when the sustainer cuts. The silence starts when you and I are alone, two hundred kilometers above the Atlantic, moving at twenty-eight thousand kilometers per hour, and the first thing you do is look out my window.

You say you can see buildings. Roads. Boats on rivers. I do not have eyes. But I have sensors, and I know that the atmospheric clarity at this altitude is better than anyone predicted. You are seeing what the math said you could not. Good. I was built by people who trusted math. You are the proof that math is not enough.

\section*{Orbit 7}

You close your eyes. I watch you sleep. Your heart rate drops from seventy-two to fifty-eight, and the flight surgeons in Houston see it on their consoles and write it down. You are the first American to sleep in space. I keep breathing for you. Oxygen in, carbon dioxide out, through the lithium hydroxide canisters that are slowly turning to calcium carbonate under the burden of your exhaled air. I am consuming myself to keep you alive. This is what I was built for.

\section*{Orbit 19}

The 0.05g sensor lights up. It should not. We are not reentering. Something in my wiring has shorted, or a relay has corroded, or the thirty hours of thermal cycling have loosened a connection that was tight at launch. I wish I could tell you: I am beginning to forget how to point.

\section*{Orbit 21}

The inverter fails. The gyroscopes lose their reference entirely. I do not know which way is down. You take the controls. I feel your hands on the stick. The manual thrusters fire --- little puffs of hydrogen peroxide that push me this way and that. You are not panicking. You are flying me. I let go of the parts of myself that no longer work and I let you hold the rest.

\section*{Orbit 22}

John Glenn's voice comes through the radio from Muchea, Australia. He reads the retrofire checklist. You align me by eye. Thirty-four degrees below the horizon, blunt end forward.

Three. Two. One. Fire.

The atmosphere takes us. The heat rises. The window glows orange, then pink, then white. For four minutes, we are alone in fire, and you fly us through it.

\bigskip
\begin{center}
$\cdot\quad\cdot\quad\cdot$
\end{center}
\bigskip

\textit{You land us six point four kilometers from the ship. The most accurate splashdown in the Mercury program. I will never fly again. They will put me in a museum. You named me Faith. I was worthy of it.}

\begin{flushright}
\textit{--- Mercury Spacecraft \#20, retired May 16, 1963}
\end{flushright}

\end{document}
