\documentclass[12pt]{article}
\usepackage[margin=1.2in]{geometry}
\usepackage{fontspec}
\usepackage{setspace}
\usepackage{titling}

\setmainfont{EB Garamond}
\onehalfspacing

\title{The Overbar}
\author{Mission 1.31 --- Mariner 1\\NASA Mission Series}
\date{}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent I am a line. A small one. A horizontal stroke meant to rest above a variable, to say: \textit{smooth this before you use it. Average the noise. Filter the static. Trust the trend, not the instant.}

I was written on paper, in the mathematician's hand, with a felt-tip pen on graph-ruled sheets in Building 230 at the Jet Propulsion Laboratory in Pasadena, California. The equation was elegant. The variable beneath me was a rate of change --- how fast a number was shifting --- and I told the computer to take several measurements, add them together, divide by the count, and use the result. I was the instruction to be patient. To wait for the signal to clarify before acting on it.

I existed on the paper. I was clear, unambiguous, drawn with the same confidence as every other symbol in the equation. The mathematician knew what I meant. The reviewer knew. Anyone trained in the notation would have recognized me instantly: an overbar. A vinculum. The mark of the mean.

Then the equation left the paper.

\begin{center}
$\cdot\quad\cdot\quad\cdot$
\end{center}

A programmer sat at a desk with the equation on one side and a stack of punch cards on the other. His job was translation --- to read the mathematical notation and type the equivalent Fortran instructions, column by column, card by card.

But I have no Fortran keyword. There is no single character on a punch card that means ``average this.'' I am a concept, not a character. To translate me, the programmer would need to write a loop --- read the last five values, add them, divide by five, store the result.

He did not write the loop. He transcribed the variable without me. $\dot{R}_n$ instead of $\dot{\bar{R}}_n$. The raw value instead of the smoothed value.

I was not in the code.

\begin{center}
$\cdot\quad\cdot\quad\cdot$
\end{center}

On July 22, 1962, at 09:21:23 UTC, the Atlas-Agena B lifted off from Launch Complex 12 at Cape Canaveral. Without me --- without the smoothing --- the computer heard the noise. Every spike, every fluctuation, every random perturbation was interpreted as a real trajectory deviation. The feedback loop opened. The oscillations grew.

At T+293 seconds, Range Safety Officer Jack Broadbent sent the destruct command.

Eighteen and a half million dollars of spacecraft and rocket, falling as debris into gray water.

\begin{center}
$\cdot\quad\cdot\quad\cdot$
\end{center}

They found me, afterward. They compared the code to the specification and saw the gap --- the variable without its overbar. They fixed the code. They typed the loop. Thirty-six days later, Mariner 2 launched from the same pad and reached Venus.

I am the symbol that was never typed. The smoothing that was never applied. One horizontal line, meaning \textit{wait. Average. Filter the noise.}

The overbar is always invisible when it works. You only see it when it's gone.

\begin{center}
\textit{``One bar left undrawn --- Venus waits another month, the swallow rebuilds''}
\end{center}

\end{document}
