\documentclass[12pt, letterpaper]{article}
\usepackage[margin=1.2in]{geometry}
\usepackage{ebgaramond}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{titling}
\usepackage{fancyhdr}

\setlength{\parindent}{2em}
\onehalfspacing

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textit{The First Astronaut}}
\fancyhead[R]{\small\textit{NASA Mission Series v1.17}}
\fancyfoot[C]{\small\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\title{\Huge\textbf{The First Astronaut}\\[0.5em]\large\textit{A short story from Mission 1.17 --- Mercury-Redstone 2}}
\author{NASA Mission Series\\[0.3em]\small Miles Tiberius Foxglove --- Mukilteo, WA}
\date{March 30, 2026}

\begin{document}
\maketitle
\thispagestyle{empty}

\vspace{1em}
\noindent\rule{\textwidth}{0.4pt}
\vspace{1em}

\noindent The couch was warm. It had been warm for a long time. Before the warm couch there had been the cold room with the metal floor, and before that the truck that vibrated, and before the truck the building where the lights were always on and the food came through slots and the levers were everywhere. The levers were the thing. The levers were what mattered. When the blue light came on, you pulled the lever. If you pulled the lever fast enough, nothing happened. If you were slow, the floor buzzed.

He had learned this a long time ago. Not learned the way the men in white coats thought he learned --- not as a sequence of stimulus and response, not as operant conditioning, not as any of the words they wrote on clipboards while watching him through glass. He had learned it the way any animal learns anything: the floor buzzes, and you don't want the floor to buzz, so you pull the lever before the floor buzzes. The blue light means the floor is about to buzz. Pull the lever when the blue light comes on. This was not complicated. This was obvious. Every animal in the forest knew things like this. The snake that vibrates its tail knows when the shadow falls. The bird that screams knows when the hawk circles. The knowing is in the body before it is in the mind.

\begin{center}
$\bullet\quad\bullet\quad\bullet$
\end{center}

The couch held him flat on his back. Straps across his chest, his hips, his legs. He could move his arms. His right hand rested near the lever. The lever was the same as the lever in the building. Same shape. Same resistance. Same satisfying click. The men had made sure of this. They had tested him on this lever a thousand times, two thousand times, until the pulling was as automatic as breathing, until blue light meant pull in the same way that falling means catch yourself. They had tested him upside down, spun him in a centrifuge, shaken him on a vibration table. He had pulled the lever through all of it.

Now the couch was vibrating. Not the way the vibration table vibrated --- that was mechanical, precise, a machine doing what machines do. This vibration was alive. It came from below and it came from everywhere and it was getting louder and the couch was shaking and something was pushing him down into the padding. The pushing was familiar. The centrifuge pushed like this. But the centrifuge was a smooth push, a steady hand pressing you into the seat. This push was rough. It stuttered. It surged. It was like being sat on by something enormous that was also on fire.

\begin{center}
$\bullet\quad\bullet\quad\bullet$
\end{center}

The blue light came on.

He pulled the lever.

The light went off. The floor did not buzz. Good. This was the same as the building. The building was shaking and roaring but the lever was the same. Pull when blue. He waited. The pushing was getting harder. His arm was heavy. His chest was heavy. Breathing was work now. Each breath was like breathing through wet cloth, like the air itself had become thick and reluctant.

The blue light came on again.

He pulled the lever. It was harder to pull. His arm weighed more than it had weighed in the building. But the lever clicked. The light went off.

The pushing increased. His vision narrowed. Not black at the edges --- not the way sleep narrows the world --- but gray, compressed, as if the world were being squeezed through a pipe. The roar was in his teeth now. The roar was in his bones. The couch was the world and the world was shaking.

\begin{center}
$\bullet\quad\bullet\quad\bullet$
\end{center}

Then a bang. A new pushing. Harder than before --- sudden, sharp, a punch added to the press. The roar changed pitch, higher, angrier, and the push increased and his body was made of stone and his arm was made of stone and the lever was at the end of a stone arm that he dragged through thickened air to the click.

Blue light. Pull. Click. Off.

He did not know that the abort system had fired. He did not know what an abort system was. He did not know that the escape rocket had ignited and that the trajectory had changed and that he was now going higher and faster than anyone had planned. He knew that the pushing was worse. He knew that the roar was different. He knew that the lever still clicked when he pulled it. These were the facts available to him, and they were sufficient.

\begin{center}
$\bullet\quad\bullet\quad\bullet$
\end{center}

The pushing stopped.

It did not taper off. It stopped. One moment he was pinned to the couch by invisible weight and the next moment the weight was gone and he was floating against the straps and his arms were lifting and the world was silent. The silence after the roar was like deafness. The silence was louder than any sound because it was the absence of something that had been so present it had become the world.

He floated. The straps held him to the couch but his body wanted to lift. His arms drifted upward. His fingers uncurled. The feeling was not unpleasant. It was like water without water, like falling without falling, like the moment at the top of a jump when you belong to nothing.

The blue light came on.

His arm floated to the lever. In the building, pulling the lever was a downward motion, gravity helping, muscles fighting. Here the lever was sideways and nowhere and his arm moved like a thing made of air. He pulled. Click. Off. The motion was strange but the click was the same. The click was always the same. The click was the fixed point in a world that had lost all its fixed points.

Six minutes and thirty-six seconds of this. Six minutes and thirty-six seconds of floating and silence and the blue light and the lever and the click. He did not count the seconds. He did not know about seconds. He knew: light, pull, click. Light, pull, click. The world was simple and the lever was reliable and the silence held him like a hand he could not see.

\begin{center}
$\bullet\quad\bullet\quad\bullet$
\end{center}

Then the pushing came back.

It came back like a wall. One moment floating, the next moment pressed flat, harder than before, harder than the centrifuge had ever pressed, harder than anything. His vision went narrow and gray and his chest could not expand and the air would not come and the roar was back but it was a different roar --- not the mechanical scream of the engine but the friction roar of the world itself resisting his passage through it. He was a stone thrown back into the atmosphere and the atmosphere was furious.

The blue light came on. His arm was impossible. His arm was a bridge made of granite that he had to lift with muscles made of rubber. But the lever was there. The lever was always there. He reached. He pulled. Click.

Fourteen times his own weight. The men would measure this later and write 14.7 on their clipboards and look at each other and shake their heads. A human would have been unconscious. A human would have been seeing black. He saw gray. He saw the light. He pulled the lever.

\begin{center}
$\bullet\quad\bullet\quad\bullet$
\end{center}

\textit{In the coastal forests of the Pacific Northwest, the rough-skinned newt crawls through leaf litter with its orange belly pressed to the earth. When a predator finds it --- a garter snake, a curious raccoon --- the newt does not run. It curls backward, exposing the bright orange underside. This is the unken reflex: the display of warning. The orange says: I am poison. The orange says: tetrodotoxin. The orange says: touch me and the signals in your nerves will stop. The newt does not know the word tetrodotoxin. The newt knows: curl, show orange, survive. The knowing is in the body.}

\begin{center}
$\bullet\quad\bullet\quad\bullet$
\end{center}

The pushing eased. The roar eased. Something banged above him and the couch jolted and then swayed and the swaying was gentle, pendular, back and forth like the branch of a tree in wind. He was hanging from something. The world was still gray at the edges but it was widening now, the pipe opening, the squeeze releasing.

Then water.

Not water on him --- water around him, the impact of a hard landing in something that was not land. The couch jolted. His body slammed against the straps and then bounced and then settled. The world rocked. The rocking was different from the vibration, different from the pushing, different from the floating. The rocking was slow and organic and it smelled like salt and distance.

He waited. He had been trained to wait. After the sequence ended, you waited, and the men came and opened the hatch and gave you an apple. The sequence had ended. He waited.

The blue light did not come on. The lever sat at the end of his arm, unneeded. The silence was different from the floating silence --- this silence had waves in it, and wind, and the creak of metal in water.

\begin{center}
$\bullet\quad\bullet\quad\bullet$
\end{center}

When the hatch opened, the light was blinding. Florida sunlight and salt air and men in uniforms reaching in with gloved hands. They lifted him out. He looked at the sky --- blue, enormous, unpressurized --- and he looked at the ocean --- green and gray and endless --- and he looked at the men who were holding him and he did not understand what he had done.

He did not know he had gone higher than any primate had ever gone. He did not know that he had crossed the line between atmosphere and space and returned. He did not know that in three weeks a man named John Glenn would sit in the same couch and fly because Ham had flown first and pulled the lever and proved that a mind could work while a body was pressed flat by fourteen times its own weight. He did not know that the men were smiling because he was alive and because his data was good and because the lever had clicked every time.

He knew: the light came on and he pulled the lever and the floor did not buzz and now the hatch was open and there would be an apple.

\begin{center}
$\bullet\quad\bullet\quad\bullet$
\end{center}

\textit{Franz Schubert died at thirty-one with two movements of a symphony on his desk. He had sketched a third but never orchestrated it. The piece became known as the Unfinished Symphony --- the most famous incomplete work in music. It is not unfinished because Schubert failed. It is unfinished because the two movements that exist are so complete in themselves that the absence of the rest becomes part of the work. The silence after the second movement is not emptiness. It is the space where the music would have been, and that space has its own shape.}

\textit{Ham's flight was unfinished too. Not in the sense of failure --- every objective was met, every lever pulled, every data point recorded. Unfinished in the sense that it was a prelude. The two movements of Ham's symphony --- the ascent and the return --- existed only so that a third movement could be written by someone else. Glenn orbited. Shepard flew. Grissom flew. They were the orchestra that played the movements Ham's flight had scored. The first astronaut did not know he was a composer. He knew the lever and the light and the click.}

\begin{center}
$\bullet\quad\bullet\quad\bullet$
\end{center}

They gave him the apple. He ate it on the deck of the USS Donner while seventeen men watched. It was a good apple. It was the same kind of apple they always gave him. He ate it in the January sunlight and the Atlantic wind and he did not look at the sky because the sky was just the sky and he was not an astronaut. He was an animal who had done what he was trained to do, in a place where training was the only thing that mattered, and the floor had not buzzed, not once, not even when the world was made of stone and the air was made of fire and the silence lasted longer than he had known silence could last.

He finished the apple. He looked at the men. He waited for the next blue light.

\vspace{2em}
\begin{center}
\textit{Dedicated to Franz Schubert (1797--1828)}\\[0.3em]
\textit{The Unfinished Symphony --- two movements, complete in their incompleteness.}\\[0.3em]
And to Ham (\#65), who pulled the lever.
\end{center}

\vspace{1em}
\noindent\rule{\textwidth}{0.4pt}
\begin{center}
\small NASA Mission Series v1.17 --- Mercury-Redstone 2\\
\small March 30, 2026
\end{center}

\end{document}
